Pulsar Acceleration Shifts from nearby Supernova Explosion

### 2015-12-20 draft3_TC.tex
added line of sight discussion

>>>>

At the instant the SNe is detected at earth, for example from direct neutrino detection, one either needs a distance measurement, or uses the pulsar timing effect to infer a distance.   All pulsar timing periodic derivatives change, proportionate to their distance to the SN.  The effect receives equal logarthmic contributions in detectability as a distance of the pulsar from the SN: in a disk population, the number of pulsars increases as the square of the distance from the SN, the effect decreases as the distance, and the sensitivity increases with the square root of the number of pulsars.  Pulsars near the line of sight will increasingly show the second acceleration change, the soonest typically after a year, for the pulsar one galactic scale length from the SN along our line of sight.  THe timing impact will be weak due to its distance from the SN, and waiting for a decade increases both the acceleration sensitivity due to the longer time baseline, and increases the likelihood of finding a pulsar closer to the SNe.
